### 2021-11-19 input/implementation.tex
not much

\begin{asparadesc}
\item [Lazy partitioning:] \TODO{Meow.}
\end{asparadesc}

@@

Next Section provides the details of our simulations that assess the
proposed implementation.

>>>>

\begin{asparadesc}
\item [Lazy partitioning:]
  To enable lazy partitioning in networks of networks, we designed and
  implemented \NAMEC (stands for both \underline{cross}
  \underline{a}utonomous \underline{s}ystems and \underline{ex}tended
  \underline{a}daptive \underline{s}coped broad\underline{cast}). The
  main idea behind \NAMEC is that every node maintains two \NAME:
  \begin{inparaenum}[(i)]
\item the first maintaining the closest source intra-AS and
  acknowledges the interests of its AS;
\item the second maintaining the closest source cross-AS that also
  competes against the local closest source.
\end{inparaenum}
\NAMEC enables nodes to discard irrelevant indexes while maintaining
the closest source between connected ASes.

\end{asparadesc}

@@

Next Section provides the details of our simulations that assess the
proposed implementations.

### 2021-11-19 input/proposal.tex
meow
not much

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $W_{xy} = W_{yx}$ be the positive symmetric \underline{w}eight
  between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
  from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
  other path weight, with $|\Pi_{xx}|$ being the greatest lower bound
  of $x$, the only consistent partitioning $\mathcal{P}$ is a set of
  partitions $P_{s\in S}$ such that each \process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1}:
  \nexists P_{s_2}$ such that $|\Pi_{s_2p}| < |\Pi_{s_1p}|$.
\end{definition}

@@

\begin{theorem}[\label{theo:efb}\underline{E}ventual \underline{F}orwarding
    of \underline{B}est $(EFB) \implies CP$] Assuming reliable
  communication links where a correct \process $q$ eventually receives
  the message $m$ \underline{s}ent to it by a \process $p$ ($s_{pq}(m)
  \implies r_{q}(m)$), \processes eventually reach consistent
  partitioning if each \process eventually \underline{f}orwards
  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
  best known partition.
\end{theorem}

@@

\subsection{Lazy partitioning}
\label{subsec:lazy}

Edge infrastructures are networks of networks. \TODO{Meow.}

@@

\NAME enables indexing the closest replica of each \process without
flooding the whole network when a new replica appears or disappears.
Nevertheless, every node must partake in the indexing of each
content. When the networks accounts for billions of content, this
raises scalability issues. Inspired by the Internet topology that
comprises tens of thousands of interconnected autonomous systems
serving billions of people~\cite{nur2018crossas}, we want to further
lock-down traffic by leveraging the edges of networks as barriers, and
enable on-demand indexing.

To enable cross-network indexing, we designed and implemented \NAMEC
(stands for both \underline{cross} \underline{a}utonomous
\underline{s}ystems and \underline{ex}tended \underline{a}daptive
\underline{s}coped broad\underline{cast}). The main idea behind \NAMEC
is that every node maintains two \NAME:
\begin{inparaenum}[(i)]
\item the first maintaining the closest source intra-AS and
  acknowledges the interests of its AS;
\item the second maintaining the closest source cross-AS that also
  competes against the local closest source.
\end{inparaenum}
\NAMEC enables nodes to discard irrelevant indexes while maintaining
the closest source between connected ASes. \TODO{This section
  describes our proposal.}

>>>>

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $W_{xy} = W_{yx}$ be the positive \TODO{symmetric} \underline{w}eight
  between $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath
  from $x$ to $z$ the weight of which $|\Pi_{xz}|$ is lower than any
  other path weight, with $|\Pi_{xx}|$ being the greatest lower bound
  of $x$, the only consistent partitioning $\mathcal{P}$ is a set of
  partitions $P_{s\in S}$ such that each \process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1}:
  \nexists P_{s_2}$ such that $|\Pi_{s_2p}| < |\Pi_{s_1p}|$.
\end{definition}

@@

\begin{theorem}[\label{theo:efb}\underline{E}ventual
  \underline{F}orwarding of \underline{B}est $(EFB) \implies CP$]
  Assuming reliable communication links where a correct \process $q$
  eventually receives the message $m$ \underline{s}ent to it by a
  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
  reach consistent partitioning if each \process eventually
  \underline{f}orwards
  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
  best known partition. \TODO{setminus parent to comply with implem'.}
\end{theorem}

@@

\subsection{Lazy dynamic consistent partitioning}
\label{subsec:lazy}

In Edge infrastructures comprising tens of thousands of autonomous
systems~\cite{nur2018crossas}, only a small subset of autonomous
systems needs logical partitioning. At any time, an autonomous system
start logical partitioning when a \process from this network becomes a
source.  Then every \process from this network belongs to the
partition of its closest source not only from their own network but
that of adjacent networks that started logical partitioning as well.
At any time, an autonomous system stops logical partitioning when the
last source from this network revokes its status of
source. Eventually, all nodes from this network do not belong to any
partition and the generated traffic stops.

@@

\begin{definition}[\TODO{Lazy DCP}]

\end{definition}

To provide lazy partitioning, \emph{gateway} \nodes that link
autonomous systems together must acknowledge if there exists a source
in their network.

Must differentiate local from global when they cross the gates.

% \NAME enables indexing the closest replica of each \process without
% flooding the whole network when a new replica appears or disappears.
% Nevertheless, every node must partake in the indexing of each
% content. When the networks accounts for billions of content, this
% raises scalability issues. Inspired by the Internet topology that
% comprises tens of thousands of interconnected autonomous systems
% serving billions of , we want to further
% lock-down traffic by leveraging the edges of networks as barriers, and
% enable on-demand indexing.
